Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-01-11 paperIEEE.tex
More Intro
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@74 db7c848b-7755-4df2-b763-8796797afa52

@@

\begin{compactdesc}
\item[Damping] reduces frame-to-frame oscillations. The equal load distribution
within the region of interest assumed by the load equalizer is in reality not
equal, causing the load balancing to overshoot. Damping is a normalized scalar
defining how much of the computed delta from the previous position is applied to
the new split.
\item[Resistance] eliminates small deltas in the load balancing step. This might
help the application to cache visibility computations since the frustum does not
change each frame.
\item[Boundaries] define the modulo factor in pixels onto which a load split may
fall. Some rendering algorithms produce artefacts related to the OpenGL raster
position, e.g., screen door transparency, which can be eliminated by aligning
the boundary to the pixel repetition. Furthermore, some rendering algorithms are
sensitive to cache alignments, which can again be exploited by chosing the
corresponding boundary.
\end{compactdesc}

@@

The framerate equalizer smoothens the output frame rate of a destination channel
by instructing the corresponding window to delay its buffer swap to a minimum
time between swaps. This is regularly used for time-multiplexed decompostions,
where source channels tend to drift and finish their rendering unevenly
distributed over time. This equalizer is however fully independent of DPlex
compounds, and may be used to smoothen irregular application rendering
algorithms.

@@

We would also like to thank all supporters and contributors of
\textsf{Equalizer}, most
notably RTT, the Blue Brain Project, the University of Siegen, EVL, Dardo, TBD.

>>>>

We do present novel algorithms for parallel rendering which did not warrant a
separate publication: pixel and subpixel decompositions, dynamic frame
resolution, tunable sort-first load-balancing parameters, frame rate
equalization, thread synchronization modes for multi-threaded rendering, dynamic
focus distance and asymmetric eye positions for Virtual Reality, parallel pixel
streaming to tiled display walls, as well as a fully-fledged data distribution
API with compression and reliable multicast.

@@

\begin{compactdesc}
\item[Split Mode] configures the tile layout: horizontal or vertical stripes,
and 2D, an binary tree split alternating the split axis on each level, resulting
in compact 2D tiles.
\item[Damping] reduces frame-to-frame oscillations. The equal load distribution
within the region of interest assumed by the load equalizer is in reality not
equal, causing the load balancing to overshoot. Damping is a normalized scalar
defining how much of the computed delta from the previous position is applied to
the new split.
\item[Resistance] eliminates small deltas in the load balancing step. This might
help the application to cache visibility computations since the frustum does not
change each frame.
\item[Boundaries] define the modulo factor in pixels onto which a load split may
fall. Some rendering algorithms produce artefacts related to the OpenGL raster
position, e.g., screen door transparency, which can be eliminated by aligning
the boundary to the pixel repetition. Furthermore, some rendering algorithms are
sensitive to cache alignments, which can again be exploited by chosing the
corresponding boundary.
\end{compactdesc}

@@

The framerate equalizer smoothens the output frame rate of a destination channel
by instructing the corresponding window to delay its buffer swap to a minimum
time between swaps. This is regularly used for time-multiplexed decompositions,
where source channels tend to drift and finish their rendering unevenly
distributed over time. This equalizer is however fully independent of DPlex
compounds, and may be used to smoothen irregular application rendering
algorithms.

@@

We would also like to thank all supporters and contributors of
\textsf{Equalizer}, most notably RTT, the Blue Brain Project, the University of
Siegen, the Electronic Visualization Lab at the University of Illinois Chicago
and Dardo Kleiner.
